```{r data-generation, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
library(exams)

## FIXED-SEED variant: the same data every version (appropriate for n = 1
## tests/exams, or a practice item that's deliberately about one unchanging
## dataset/scenario). For a practice quiz (n > 1) — the common case — prefer
## `cloze_regenerated.Rmd` instead, which regenerates fresh data (and a
## fresh downloadable script) every version via rejection sampling. See
## "Per-version regenerated data" in reference/generators-and-data.md.

## Make the student script (and any CSVs) downloadable from the question.
include_supplement("cloze_mixed_paired.R")
# include_supplement("some_data.csv")     # uncomment per data file, if any

## ── Re-derive the answer key ─────────────────────────────────────────────
## Reproduce EXACTLY what a correct student would run. Use the SAME seed and
## the SAME constants as the paired .R script so the key matches their output.
set.seed(4242)
n     <- 60
mu    <- 100
sigma <- 15

x <- rnorm(n, mean = mu, sd = sigma)

ans_mean  <- round(mean(x), 4)              # (a) sample mean
ans_var   <- round(var(x),  4)              # (b) sample variance (n-1 denom)
ans_se    <- round(sd(x) / sqrt(n), 4)      # (c) standard error of the mean

## ── Conceptual schoice blanks ────────────────────────────────────────────
## Each opts_* is a length-4 character vector; the matching sol_* is logical
## with exactly one TRUE. Build distractors that encode real misconceptions.
## DO NOT put a `~` inside any option string — it is the cloze separator.
opts_d <- c(
  "The standard error of the sample mean is $\\sigma / \\sqrt{n}$; it shrinks as the sample size grows, so larger samples give more precise estimates of $\\mu$.",
  "The standard error of the sample mean equals the sample standard deviation $s$; it does not depend on the sample size, only on the spread of the data.",
  "The standard error of the sample mean is $\\sigma^2 / n$; it has the units of a variance, not of the original measurements.",
  "The standard error of the sample mean grows with $n$, because summing more observations accumulates more sampling variability."
)
sol_d <- c(TRUE, FALSE, FALSE, FALSE)

opts_e <- c(
  "By the Central Limit Theorem, the sampling distribution of $\\bar{X}$ is approximately normal for large $n$ regardless of the shape of the population distribution.",
  "The sampling distribution of $\\bar{X}$ is normal only if every individual observation is itself drawn from a normal distribution; no approximation holds otherwise.",
  "The sampling distribution of $\\bar{X}$ becomes more skewed as $n$ increases, because extreme observations dominate the average.",
  "The sampling distribution of $\\bar{X}$ has the same variance as the population, since averaging does not change the spread."
)
sol_e <- c(TRUE, FALSE, FALSE, FALSE)

## ── Assemble the option list and the per-blank solution strings ──────────
all_opts <- c(opts_d, opts_e)               # order must match the schoice markers
sol_strings <- c(
  mchoice2string(sol_d, single = TRUE),
  mchoice2string(sol_e, single = TRUE)
)

## ── Build the meta vectors dynamically so they can never drift ───────────
types <- c("num", "num", "num", "schoice", "schoice")
tols  <- ifelse(types == "num", "0.005", "0")
```

Question
========

<hr>
<mark>
**NOTE:** Right-click and "Save link as" to download
[**cloze_mixed_paired.R**](cloze_mixed_paired.R) into a working directory of
your choice. Complete every section marked `your_code_goes_here()` and then
run the script with **Source**.
</mark>
<hr>

**Scenario.** You draw a single sample of $n = `r n`$ observations from a
normal population with mean $\mu = `r mu`$ and standard deviation
$\sigma = `r sigma`$. The seed `set.seed(4242)` is fixed in the script.
Round numerical answers to **four decimal places**.

---

**(a)** Report the **sample mean** of `x`.

##ANSWER1##

**(b)** Report the **sample variance** of `x` (the $n - 1$ denominator).

##ANSWER2##

**(c)** Report the **standard error of the sample mean**, $s / \sqrt{n}$.

##ANSWER3##

**(d)** Which statement correctly describes the standard error of the sample mean?

##ANSWER4##

**(e)** Which statement correctly describes the sampling distribution of $\bar{X}$?

##ANSWER5##

```{r questionlist, echo=FALSE, results="asis"}
answerlist(all_opts, markup = "markdown")
```

Solution
========

**(a)** Sample mean $\approx$ `r ans_mean`. In R: `mean(x)`.

**(b)** Sample variance $\approx$ `r ans_var`. In R: `var(x)`, which uses the $n - 1$ denominator.

**(c)** Standard error $= s / \sqrt{n} \approx$ `r ans_se`. In R: `sd(x) / sqrt(length(x))`.

**(d)** The standard error of the mean is $\sigma / \sqrt{n}$ (estimated by $s / \sqrt{n}$); it decreases as $n$ grows.

**(e)** By the Central Limit Theorem, $\bar{X}$ is approximately normal for large $n$ whatever the population shape.

```{r solutionlist, echo=FALSE, results="asis"}
answerlist(ifelse(c(sol_d, sol_e), "Correct.", "Incorrect."), markup = "markdown")
```

Meta-information
================
extype: cloze
exclozetype: `r paste(types, collapse = "|")`
exsolution: `r paste(c(ans_mean, ans_var, ans_se, sol_strings), collapse = "|")`
extol: `r paste(tols, collapse = "|")`
exname: Sampling distribution of the mean
exshuffle: TRUE
