```{r data-generation, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
library(exams)

## PER-VERSION variant (the DEFAULT for practice quizzes, n > 1): fresh data
## AND a freshly customised downloadable script every version, via rejection
## sampling. For n = 1 tests/exams, or a practice item deliberately about one
## unchanging dataset, use the fixed-seed `cloze_mixed.Rmd` template instead.
## See "Per-version regenerated data" in reference/generators-and-data.md.

## ── compute(seed): EXACTLY what the finished student script does ─────────
## Its return value is both this version's answer key AND what the
## rejection loop below inspects to decide whether to accept the seed.
compute <- function(seed) {
  set.seed(seed)
  n <- 60
  x <- rnorm(n, mean = 50, sd = 10)
  y <- 3 + 0.8 * x + rnorm(n, mean = 0, sd = 5)
  fit <- lm(y ~ x)

  list(
    slope = round(unname(coef(fit)["x"]), 4),
    r2    = round(summary(fit)$r.squared,  4)
  )
}

## ── Per-version seed: rejection-sample so the story is clean ─────────────
## Accept only seeds giving a strong, unambiguous, positive slope — adjust
## the bounds to whatever this question's narrative actually needs. Keep
## the check as loose as the pedagogy allows; over-constraining just makes
## the loop slower (or, worst case, non-terminating).
repeat {
  seed <- sample(10000:99999, 1)
  a <- compute(seed)
  if (a$r2 >= 0.5 && a$slope > 0) break
}

## ── Write THIS version's student script and attach it for download ───────
## __SEED__ (and any other __PLACEHOLDER__s) are substituted per version;
## everything else in the template is identical across versions.
script_template <- '# ============================================================================
# MODULE Practical - <topic>: <one-line scenario>
# ============================================================================
#
# Scenario: <describe the scenario in plain English>.
#
# HOW TO USE THIS SCRIPT
#   1. Replace every your_code_goes_here() with your own code.
#   2. Do NOT change the data block or the set.seed(...) lines: the seed keeps
#      your answers identical to the marking key.
#   3. Run the whole script with Source. Enter the printed values into Moodle.
#
# Round numeric answers to FOUR decimal places.
# ============================================================================

your_code_goes_here <- function(...) {
  stop("Placeholder not replaced. Replace each your_code_goes_here() with your own code.")
}

# -- Data generation (do NOT change) -----------------------------------------
set.seed(__SEED__)
n <- 60
x <- rnorm(n, mean = 50, sd = 10)
y <- 3 + 0.8 * x + rnorm(n, mean = 0, sd = 5)

# -- Step 1: fit the model -----------------------------------------------------
fit <- your_code_goes_here()   # Consult ?lm; regress y on x.

# -- Step 2: read off the slope and R-squared ---------------------------------
slope <- your_code_goes_here() # Pull the x coefficient out of the coefficients of fit.
r2    <- your_code_goes_here() # Consult ?summary.lm for the R-squared component.

# -- Report the values to enter into Moodle ----------------------------------
writeLines(c(
  paste("Slope of x  :", round(slope, 4)),
  paste("R-squared   :", round(r2,    4))
))
'
writeLines(gsub("__SEED__", seed, script_template, fixed = TRUE), "cloze_regenerated.R")
include_supplement("cloze_regenerated.R")

## ── Conceptual schoice blank (optional, same rules as cloze_mixed.Rmd) ───
opts_c <- c(
  "A larger R-squared here means x explains a larger share of the variation in y.",
  "R-squared measures the strength of a causal effect, not just association.",
  "R-squared always increases as n grows, regardless of the true relationship.",
  "R-squared close to the slope's own value is a coincidence with no meaning."
)
sol_c <- c(TRUE, FALSE, FALSE, FALSE)

types <- c("num", "num", "schoice")
tols  <- c("0.005", "0.005", "0")
```

Question
========

<hr>
<mark>
**NOTE:** Right-click and "Save link as" to download
[**cloze_regenerated.R**](cloze_regenerated.R) into a working directory of
your choice. Complete every section marked `your_code_goes_here()` and then
run the script with **Source**. Enter the printed values below. **Do not
change the seed.**
</mark>
<hr>

**Scenario.** <Describe the scenario in plain English; state $n$ and any fixed
constants explicitly since they appear, version-specific, in the download.>
Round numeric answers to **four decimal places**.

---

**(a)** Estimated **slope** of `x`:

##ANSWER1##

**(b)** **R-squared** of the fitted model:

##ANSWER2##

**(c)** Which is the correct interpretation of your R-squared?

##ANSWER3##

```{r questionlist, echo=FALSE, results="asis"}
answerlist(opts_c, markup = "markdown")
```

Solution
========

Running the completed script (the seed is fixed inside it) gives:

- **(a)** Slope of `x` $\approx$ `r a$slope` — `coef(fit)["x"]`.
- **(b)** R-squared $\approx$ `r a$r2` — `summary(fit)$r.squared`.
- **(c)** A larger R-squared means `x` explains a larger share of the variation
  in `y` — it does **not** by itself establish causation, and it is not
  guaranteed to grow with `n`.

```{r solutionlist, echo=FALSE, results="asis"}
answerlist(ifelse(sol_c, "Correct.", "Incorrect."), markup = "markdown")
```

Meta-information
================
extype: cloze
exclozetype: `r paste(types, collapse = "|")`
exsolution: `r paste(c(a$slope, a$r2, mchoice2string(sol_c, single = TRUE)), collapse = "|")`
extol: `r paste(tols, collapse = "|")`
exname: <Short descriptive name>
exshuffle: TRUE
